Source Summaries

### 2020-04-20 paper/sourceSummaries/summary9.tex
added joshua's 9th source summary

@@

@@

@@

@@

@@

>>>>

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{5116218}

@@

\noindent
The authors analyze the encryption of the Bluetooth protocol and highlight insecure elements in the design.  The authors also highlight how these problems could be fixed.

@@

\noindent
Game Theory.  The authors are theoretically attacking the encryption standard used in bluetooth.

@@

\noindent
The authors reviewed elements of the Bluetooth encryption stacked, and picked out issues as they found them.

@@

\noindent
The authors found that Bluetooth can not be considered secure compared to conventional fixed networks.  There are too many implementation errors.

@@

\noindent
The authors do not specify future directions, but the paper is old by tech standards, and could be updated with information from newer bluetooth standards, like Bluetooth 5.0.
